Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-07-11 manuscripts/TCS2023/tcs2023.tex
typo

\change{Another direction to speed up our approach in the side of Boolean networks is to apply reduction techniques to the original Boolean network.
Many reduction techniques on Boolean networks~\cite{DBLP:journals/tcs/NaldiRTC11,schwieger2023reduction} have been proposed and some of them fully preserve attractors of a Boolean network under the fully asynchronous update scheme.
In particular, a reduction technique on elimination of negatively auto-regulated nodes with respect to asynchronous attractors has recently been proposed~\cite{schwieger2023reduction}.
However, there are two major issues needed to be considered.
First, the question of whether these reduction techniques fully preserve minimal trap spaces of a Boolean network is still open.
Second, although these reduction techniques can reduce the number of nodes, they can also increase the complexity of Boolean update functions~\cite{DBLP:journals/tcs/NaldiRTC11}, which is also an importan factor for the performance of computation methods.
It raises the question of whether they really simplify the computational burden of trap space computation.
We will deeply investigate the two issues.
Furthermore, we believe that the connection between trap spaces and siphons can be a very useful tool for addressing the first issue.
}

>>>>

\change{Another direction to speed up our approach in the side of Boolean networks is to apply reduction techniques to the original Boolean network.
Many reduction techniques on Boolean networks~\cite{DBLP:journals/tcs/NaldiRTC11,schwieger2023reduction} have been proposed and some of them fully preserve attractors of a Boolean network under the fully asynchronous update scheme.
In particular, a reduction technique on elimination of negatively auto-regulated nodes with respect to asynchronous attractors has recently been proposed~\cite{schwieger2023reduction}.
However, there are two major issues needed to be considered.
First, the question of whether these reduction techniques fully preserve minimal trap spaces of a Boolean network is still open.
Second, although these reduction techniques can reduce the number of nodes, they can also increase the complexity of Boolean update functions~\cite{DBLP:journals/tcs/NaldiRTC11}, which is also an important factor for the performance of computation methods.
It raises the question of whether they really simplify the computational burden of trap space computation.
We will deeply investigate the two issues.
Furthermore, we believe that the connection between trap spaces and siphons can be a very useful tool for addressing the first issue.
}
